\subsection{Data Abstraction } \label{sec:dataabstraction}

Underpinning Data Making and Data Serving is out abstraction of data and services.
This includes middleware such as  butler and batch production systems etc.
But also Prompt Processing execution and Data engineering.
It is crucial for our system portability to maintain the abstraction layer.

A comprehensive list is given in \secref{sec:products}.

Some of these require a little more discussion here.

\subsubsection{Data Engineering}

\begin{itemize}
\item Support the metadata translation infrastructure (astro\_metadata\_translator) and monitor correctness of FITS headers.
\item Advise on file formats and file metadata for all systems writing files that are to be archived.
\item Support the Felis system for specifying schemas.
\item Define the data models for everything in the consolidated database. (“global data model” schema?)
\item Write and support code that populates the consolidated database (for example, code that analyzes the EFD and creates the “exposure” and “visit” tables).
\item Gregory Dubois-Felsmann is product owner (“Data Scientist”)
\item Staffing: tiny in construction. 0.5 FTE in ops + fractional GPDF.

\end{itemize}


\subsubsection{Middleware Assumptions}
As can be seen in the product list there are a lot of elements to Middleware.
A few assumptions are made.
\begin{itemize}
\item Assumes butler/Rucio integration is entirely handled by the infrastructure team.
\item Assumes database administration is done by the infrastructure team.
\item Staffing: 0.5 Andy S; 0.5 new NateP; NateL 0.25; Matthias 0.5; MichelleG 0.5; Kowalik 0.25; at least 0.25 PanDA ongoing person for ctrl\_bps\_panda.

\end{itemize}


