\subsection{DM Science} \label{sec:dmsci}
%
The DM Science team, led by the DM Lead Scientist, is responsible for defining the vision of the DMS to meet the ten-year scientific goals of the LSST.
The team operates at the intersection of DM engineering and the scientific community to ensure the as-built DMS enables transformative science.
It works closely with DM engineering to build a system that supports the scientific potential of Rubin/LSST, while also liaising with the community to facilitate their use of DM deliverables.
By learning from the community’s experiences, the team integrates this feedback into the continuous evolution and refinement of the system.
This collaborative approach helps identify new research opportunities and ensures the DMS evolves with the scientific landscape as fresh insights emerge from LSST data releases.

The DM Science team leads the evaluation of DM performance by tracking KPIs, conducting trend analyses, and overseeing the production of Data Release papers and other key publications to ensure scientific rigor and highlight the transformative potential of LSST data products.

Within DM, the team serves as a forum for addressing cross-functional issues or topics without dedicated staff, ensuring important matters are not overlooked and alignment with Rubin Observatory and LSST science goals is maintained.

Additionally, DM Science leads joint data processing efforts with other missions, such as Euclid and Roman, fostering collaboration and maximizing the scientific return from multi-mission data.

\subsubsection{DM Lead Scientist }

The DM Lead Scientist has the ultimate responsibility for ensuring DM initiatives provide solutions that meet the overall LSST science goals.
As such, this person leads the definition and understanding of the science goals and deliverables of LSST Data Management and is accountable for communicating these to the DM engineering teams, and working with the DM engineering teams to validate their deliverables.

The DM Lead Scientist reports to the Rubin Director (or Head of Science -- TBD)  and is a member of both the DM and Rubin Change Control Boards, as well as the Rubin Operations Science Team.
Additionally, the DM Lead Scientist chairs and directs the work of the DM Science Team.

Specific responsibilities and authorities include:
\begin{itemize}
\item Communicates with DM science stakeholders (Rubin directors, Scientists and Team, advisory bodies, the science community) to understand their needs and identifies aspects to be satisfied by the DM Department.
\item Communicates insights from DM across Rubin departments to inform system-wide decision-making and enhance the understanding of overall system performance.
\item Develops, maintains, and articulates the vision of DM products and services responsive to stakeholder needs.
\item Communicates the DM System vision to DM stakeholders. Works with the DMAD to communicate and articulate the DM System vision, requirements and especially priorities  to the DM  team.
\item Develops and/or evaluates proposed changes to DM deliverables driven by schedule, budget, or other constraints.
\item Validates the science quality of DM deliverables and the capability of all elements of the DM System to achieve LSST science goals with the V\&V team.
\item Serves as Data Management Liaison as requested by Science Collaborations or agrees delegates.
\item Defines the science acceptance criteria for DM deliverables (both final and intermediate) and validates that they have been met (Science Validation).
\item Delegates authority and responsibility as appropriate to other DM Science Leads
\item Represents and speaks for Rubin  Data Management.
\item Convenes and/or participates in all DM reviews.
\item Co-Chairs the DM Executive
\item Leads joint data processing efforts with other missions, such as Euclid and Roman,
\end{itemize}

\subsubsection{Community Science}


