\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{Algorithm and Pipeline roles for Rubin Observatory Data Management Operations \label{tab:apfroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.8a}&{Algorithms \& Pipelines Lead}&{Responsible for the leadership and coordination of the Data Production Team, the scientific integrity of Alert Production and Data Releases, and interaction and coordination with the Lead Community Scientist, Lead Scheduler Scientist, and the Lead Production Scientist. This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience, or a software engineer with extensive astronomical experience.} \\ \hline
{3.8b}&{Alert Production Pipeline Group Leader}&{Applying extensive astronomical knowledge, including solar system, explosive transients, and time-domain surveys in general, and Rubin Observatory software experience, this role acts as product owner for the prompt processing pipelines and oversees the day-to-day work of the Alert Production Pipeline Scientists. Recommends changes to Alert Production Pipelines and supports or rejects software changes based on scientific validation of new algorithms and an understanding of their impact on required computational resources. This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience or a software engineer with extensive astronomical expertise.} \\ \hline
{3.8c}&{Lead Alert Production Algorithms Scientist}&{This role provides leadership for the algorithmic development of the prompt processing pipelines, such as image differencing and template generation. This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience or a software engineer with extensive astronomical expertise.} \\ \hline
{3.8d.1}&{Alert Production Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific prompt processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Prompt Processing Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive time-domain survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Alert Production Pipeline Group Leader.} \\ \hline
{3.8d.2}&{Alert Production Pipeline Scientist - SLAC}&{This role combines an understanding of one or more specific prompt processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Prompt Processing Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive time-domain survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Alert Production Pipeline Group Leader.} \\ \hline
{3.8e}&{Alert Production Pipeline Consultant}&{Supports and reports to the Alert Production Pipeline Group Leader. The Consultant position is a senior software position filled by fractions of individuals with deep and intimate knowledge of the Rubin Observatory Data Management system, presumably from the construction period.  Guidance for the solar system processing pipeline. } \\ \hline
{3.8f}&{AVS Oversight Liaison}&{A member of the Alert Production Pipeline Group should work closely with the AVS Engineers to ensure proper integration of the algorithms and correct application of any data screening. } \\ \hline
{3.8g}&{Data Release Pipeline Group Leader}&{Applying extensive astronomical knowledge of all key Rubin Observatory science cases  (including dark energy, galaxies, and stars), wide-field astronomical surveys, and Rubin Observatory software, this role acts as product owner for the data release processing pipelines and oversees the day-to-day work of the Data Release Pipeline Scientists. Recommends changes to Data Release Production Pipelines and supports or rejects software changes based on scientific validation of new algorithms and an understanding of their impact on required computational resources. Defines, develops, and maintains the Rubin Observatory scientific processing pipelines' overall architecture, advising Pipeline Scientists to ensure that the overall Rubin Observatory Science Pipelines form a coherent whole, interfacing with the Middleware Team.  This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience or a software engineer with extensive astronomical expertise. Expert in software architecture with expertise in scientific software design and the Rubin Observatory software system preferred.  Reports to the Lead of Algorithms and Pipelines. } \\ \hline
{3.8h.1}&{Data Release Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.} \\ \hline
{3.8h.2}&{Data Release Pipeline Scientist - SLAC}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.} \\ \hline
{3.8i}&{Science Pipelines Release Engineer}&{Maintain and improve the builds for the various Data Management Operations software products. This includes fixing the continuous integration builds and improving the packaging system (currently aiming for Conda but could potentially move to another system over ten years). Flag features for inclusion in software releases needed for data releases. Write release notes. (This role COULD also support the observatory software builds which could potentially remain different to the Data Management Operations builds)} \\ \hline
{3.8j}&{Lead Calibration Scientist}&{Together with the Calibration Support Scientist at the summit, ensures that data is available to enable proper astrometric and photometric calibration of Rubin Observatory data as part of regular pipeline processing. The Lead Calibration Scientist reports to the Lead of the Algorithms and Pipelines Team. The Lead Calibration Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience: it is desirable for this position to be filled by a person who contributed to the construction of the Calibration Products Production pipeline.} \\ \hline
{3.8k}&{Calibration Group Leader}&{Ensures that data is available to enable proper astrometric and photometric calibration of Rubin Observatory data as part of regular pipeline processing. This role combines an understanding of one or more specific data release processing science use cases with software engineering expertise to modify, extend, and update the first steps of both the prompt processing and data release pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience. Prefer someone who contributed to the construction of the Calibration Products Production Pipeline} \\ \hline
{3.8l}&{Calibration Scientist - SLAC}&{Ensures that data is available to enable proper astrometric and photometric calibration of Rubin Observatory data as part of regular pipeline processing. This role combines an understanding of one or more specific data release processing science use cases with software engineering expertise to modify, extend, and update the first steps of both the prompt processing and data release pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience. Prefer someone who contributed to the construction of the DM Calibration Products Production Pipeline or from the construction era Camera Team} \\ \hline
{3.8m}&{Calibration Consultant}&{Advises and reports to the Calibration Group Leader. The Consultant position is a senior position filled by fractions of individuals with deep and intimate knowledge of the Rubin Observatory Data Management system, presumably from the construction period.} \\ \hline
\end{longtable} \normalsize
