\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{Chile Summit and Base Facility roles for Rubin Observatory Data Management Operations \label{tab:chdfroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.5a}&{Chilean DevOps Technical Lead/Manager}&{Responsible for technical leadership and management of the Chilean DevOps Support Team, including planning and overseeing the installation, operation and maintenance of all Chilean computing hardware. This includes all summit hardware, networks and cabling. The summit systems are run as infrastructure through service deployment; the Chilean devops team must maintain a deployment ready layer (foreman, puppet, kubernetes) for software teams to work with. This also includes maintaining the camera test stands in Chile and in Tucson in a similar as that for the summit. Interface with NOIRLab COS-IT to coordinate delivered IT services such as helpdesk and network support. Work with the I\&S Team's DF/DACs Technical Coordinator to build the Chilean DAC into the Rubin DAC Network.} \\ \hline
{3.5b}&{Chilean DevOps Engineer 11/17/2023}&{Responsible for the installation, operation and maintenance of all Chilean and test stand (Tucson) computing hardware. This includes guidance on technical decisions for technology both in terms of hardware and software. This may require negotiation/persuasion of COS/IT to support desired Rubin technology in the future and open mindedness to offered solutions from NOIRlab. Training and inclusion of less experienced staff is an essential part of this role.} \\ \hline
{3.5b.1}&{Chilean DevOps Engineer}&{Responsible for the installation, operation and maintenance of all Chilean and test stand (Tucson) computing hardware. This includes guidance on technical decisions for technology both in terms of hardware and software. This may require negotiation/persuasion of COS/IT to support desired Rubin technology in the future and open mindedness to offered solutions from NOIRlab. Training and inclusion of less experienced staff is an essential part of this role.} \\ \hline
{3.5b.2}&{Chilean DevOps Engineer Cover}&{Responsible for the installation, operation and maintenance of all Chilean and test stand (Tucson) computing hardware. This includes guidance on technical decisions for technology both in terms of hardware and software. This may require negotiation/persuasion of COS/IT to support desired Rubin technology in the future and open mindedness to offered solutions from NOIRlab. Training and inclusion of less experienced staff is an essential part of this role.} \\ \hline
\end{longtable} \normalsize
