\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{Campaign Management roles for Rubin Observatory Data Management Operations \label{tab:cmroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.9a}&{Campaign Management Lead}&{Lead the Campaign Management Team. Coordinate scheduling and training. Perform day to day technical operation of data processing campaigns, including Alert Production, Data Release Production, Calibration, and other campaigns. Diagnose and address processing deficiencies, bottlenecks, and failure modes. Coordinate with the V\&V team in testing and implementing the campaign strategies and finalizing the campaign configurations. Coordinate with the Workflow/load Management Engineer and the US DF Infrastructure Group in troubleshooting infrastructure failures. This may require 7 days per week coverage.} \\ \hline
{3.9b.2}&{Processing Scientist - SLAC}&{Perform day to day technical operation of data processing campaigns, including Alert Production, Data Release Production, Calibration, and other campaigns. Diagnose and address processing deficiencies, bottlenecks, and failure modes. Coordinate with the V\&V team in testing and implementing the campaign strategies and finalizing the campaign configurations. Coordinate with the Workflow/load Management Engineer and the Infrastructure Group in troubleshooting infrastructure failures. This may require 7 days per week coverage.} \\ \hline
{3.9b.1}&{Processing Scientist - NOIRLab}&{Perform day to day technical operation of data processing campaigns, including Alert Production, Data Release Production, Calibration, and other campaigns. Diagnose and address processing deficiencies, bottlenecks, and failure modes. Coordinate with the V\&V team in testing and implementing the campaign strategies and finalizing the campaign configurations. Coordinate with the Workflow/load Management Engineer and the Infrastructure Group in troubleshooting infrastructure failures. This may require 7 days per week coverage.} \\ \hline
{3.9b.3}&{Processing Scientist - IN2P3}&{Perform day to day technical operation of data processing campaigns, including Alert Production, Data Release Production, Calibration, and other campaigns. Diagnose and address processing deficiencies, bottlenecks, and failure modes. Coordinate with the V\&V team in testing and implementing the campaign strategies and finalizing the campaign configurations. Coordinate with the Workflow/load Management Engineer and the Infrastructure Group in troubleshooting infrastructure failures. This may require 7 days per week coverage.} \\ \hline
{3.9b.4}&{Processing Scientist - UK}&{Perform day to day technical operation of data processing campaigns, including Alert Production, Data Release Production, Calibration, and other campaigns. Diagnose and address processing deficiencies, bottlenecks, and failure modes. Coordinate with the V\&V team in testing and implementing the campaign strategies and finalizing the campaign configurations. Coordinate with the Workflow/load Management Engineer and the Infrastructure Group in troubleshooting infrastructure failures. This may require 7 days per week coverage.} \\ \hline
{3.9c.2}&{Campaign Management Developer - SLAC}&{To be written!} \\ \hline
{3.9c.1}&{Campaign Management Developer - NOIRLab}&{To be written!} \\ \hline
\end{longtable} \normalsize
