\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{Data Engineering roles for Rubin Observatory Data Management Operations \label{tab:deroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.7a}&{Data Scientist}&{Hold project history on data models etc and guide VO developments} \\ \hline
{3.7b.1}&{Data Engineer - NOIRLab}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.} \\ \hline
{3.7b.2}&{Data Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.} \\ \hline
{3.7c}&{Build Engineer  - 11/17/2023}&{Maintain and improve the builds for the various Data Management Operations software products. This includes fixing the continuous integration builds and improving the packaging system (currently aiming for Conda but could potentially move to another system over ten years). With hundreds of packages this is not a trivial task. This role would also support the observatory software builds which could potentially remain different to the Data Management Operations builds.} \\ \hline
{3.7c.1}&{Build Engineer }&{Maintain and improve the builds for the various Data Management Operations software products. This includes fixing the continuous integration builds and improving the packaging system (currently aiming for Conda but could potentially move to another system over ten years). With hundreds of packages this is not a trivial task. This role would also support the observatory software builds which could potentially remain different to the Data Management Operations builds.} \\ \hline
{3.7c.2}&{Build Engineer }&{Maintain and improve the builds for the various Data Management Operations software products. This includes fixing the continuous integration builds and improving the packaging system (currently aiming for Conda but could potentially move to another system over ten years). With hundreds of packages this is not a trivial task. This role would also support the observatory software builds which could potentially remain different to the Data Management Operations builds.} \\ \hline
\end{longtable} \normalsize
