\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{FRDF roles for Rubin Observatory Data Management Operations \label{tab:frdfroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.2e.3}&{Data Wrangler - IN2P3}&{The data wrangler ensures that data (science raw data, calibration data, data products, etc.) is replicated at IN2P3 and data products resulting from the local processing performed at IN2P3 are replicated to the USDF They also ensure that the data archived at IN2P3 and needed for the annual processing are recalled from tape on time for the image processing tasks to be performed. They ensure that the tools and systems used for replicating data at IN2P3 are operational. This role needs tight coordination with the team at the USDF that is responsible for data distribution.} \\ \hline
{3.2l.3}&{Image Handler - IN2P3}&{The image handler ensures the image processing stages assigned to IN2P3 are performed on time. This person also ensures that the processing (e.g. software releases, configuration files, etc.) is compatible with what is agreed upon with the other processing sites, in particular with the USDF. They also ensure that IN2P3's image processing infrastructure (batch processing, workflow management system, etc.) is operational and correctly configured for LSST needs. They also ensure the day-to-day operations of the annual image processing campaign. This role needs tight coordination with the team in charge of image processing at the USDF.} \\ \hline
{3.2g.3}&{Catalog Manager - IN2P3}&{The catalog manager ensures the day-to-day operations of the astronomical catalog database at IN2P3. This includes ingesting new data and removing and archiving obsolete catalogs. They also interact with the data wrangler to ensure that the catalog data produced at other sites are imported and ingested into the IN2P3 catalog and that the catalog data produced at IN2P3 is ingested into the local catalog and replicated to other sites. They also ensure that the software releases for the catalog database are compatible with those releases used at other sites operating a catalog database, in particular, the USDF.} \\ \hline
\end{longtable} \normalsize
