\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{Management roles for Rubin Observatory Data Management Operations \label{tab:mroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.1a}&{Associate Director for Data Management Operations}&{The AD of the Data Management Operations Department is one of the principal leaders of the Rubin Observatory operations phase. This position requires a Ph.D. level astronomer with extensive astronomical survey and science management experience, and reports directly to the Rubin Observatory Director. The primary responsibilities of this position include the management of the Data Management Operations Department (including budget and planning for this WBS element), participation in the leadership of Rubin Observatory survey, and coordination with other Rubin Observatory Departments. The AD for Data Management Operations also has overall responsibility and authority for safely running the Rubin Observatory Data Facilities (DF) including the generation of prompt data products (alerts) and the annual data release processing. This person will supervise a technical staff that will be responsible for all aspects of data processing, preparation of data products, archiving, and operation of the Chilean, French and UK DACs/DFs, as well as the US DF. They will be responsible for coordinating with project level Contract Management and Supplier Management when dealing with issues of business impact, and accountable for ensuring a disaster recovery plan is effective and able to be invoked. The AD of Data Management Operations is also responsible for supervising the data flow from the Recinto to the USDF.} \\ \hline
{3.1b}&{Data Management Operations Deputy Manager}&{Assist the AD of Data Management Operations in all aspects of the ongoing project. The deputy manager will be enabled to act on behalf of the AD in any situation.} \\ \hline
{3.1c.2}&{Data Management Operations Advisor - US DF}&{Each Rubin Observatory Data Facility (US, French and UK) has an advisory role to the AD for Data Management Operations in terms of execution across the data facilities.  The US DF Advisor role is held by the US DF Lead; this person is responsible for Data Facilities oversight, analgous to the other oversight areas in the department. } \\ \hline
{3.1c.3}&{Data Management Operations Advisor - Fr DF}&{Each Rubin Observatory Data Facility (US, French and UK) has an advisory role to the AD for Data Management Operations in terms of execution across the data facilities.  } \\ \hline
{3.1c.4}&{Data Management Operations Advisor - UK DF}&{Each Rubin Observatory Data Facility (US, French and UK) has an advisory role to the AD for Data Management Operations in terms of execution across the data facilities.  } \\ \hline
{3.1d.1}&{Data Abstraction Oversight}&{Oversees the Pipeline Middleware and Data Engineering Teams, functionally supervising the leaders of those teams and reporting on their activity to the AD for RDM. } \\ \hline
{3.1d.2}&{Data Production Oversight}&{Oversees the Algorithms and Pipelines and Campaign Management Teams, functionally supervising the leaders of those teams and reporting on their activity to the AD for RDM. } \\ \hline
{3.1d.3}&{Data Services Oversight}&{Oversees the SQuaRE and Advanced Databases Teams, functionally supervising the leaders of those teams and reporting on their activity to the AD for RDM. } \\ \hline
{3.1d.4}&{Data Acquisition Oversight}&{Oversees the SQuaRE and Advanced Databases Teams, functionally supervising the leaders of those teams and reporting on their activity to the AD for RDM. } \\ \hline
\end{longtable} \normalsize
