\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{Pipeline Middleware roles for Rubin Observatory Data Management Operations \label{tab:pmwroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.6a}&{Pipeline Middleware Lead}&{Organizes the software maintenance effort and assigns work in a way that provides for continuity of maintenance for all Rubin Observatory maintained software. Is primarily responsible for further defining and enforcing software engineering rules related to maintenance, including maintenance of documentation, correct security practices, testing, and other aspects of delivery of a complete change set. Ensures that software tasks are consistent with authorized changes. Carries share of maintenance load. Participates in reviews.} \\ \hline
{3.6b.1}&{Pipeline Middleware Engineer - NOIRLab}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.} \\ \hline
{3.6b.2}&{Pipeline Middleware Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.} \\ \hline
{3.6b.3}&{Pipeline Middleware Engineer - NOIRLab/NCSA}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.} \\ \hline
{3.6b.4}&{Pipeline Middleware Engineer - NOIRLab/Princeton}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.} \\ \hline
\end{longtable} \normalsize
