\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{SQuARE roles for Rubin Observatory Data Management Operations \label{tab:sqroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.10a}&{Technical Lead/Manager}&{Responsible for technical leadership and management of the Service Quality and Reliability Engineering Team. This includes running stand ups and looking after budgets and staff issues as well as making technical calls where decisions are needed. The technical lead is responsible overall for the architecture of the team’s services and for ensuring it is fit for purpose for the observatory’s evolving needs. They also represent the team’s work both inside the organization and to the astronomical and computing technical community.} \\ \hline
{3.10b.1}&{Senior Full Stack and Documentation Engineer - NOIRLab}&{A Senior Full-Stack Engineer is a DevOps Engineer who is versed in architecture and implementation of both backend and frontend architectures. They are able to synthesize requirements, propose system architectures and independently implement services. They have advanced skills in DevOps engineering, including Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
A Documentation Engineer is well versed in architecting effective ways to support documentation oriented workflows such as documentation continuous delivery systems and integration with communication platforms. They have advanced skills in service implementation and deployment, familiarity with documentation infrastructure libraries such as Sphinx, and best practices in software documentation, including code-level, package-level and user guides. 
} \\ \hline
{3.10b.2}&{Security Architect / Senior DevOps Engineer  - NOIRLab}&{A Security Architect is a software engineer with advanced expertise in designing and building software services with particular regard to security concerns such as authentication \& authorisation, hardening, auditability, penetration testing and dependency management.  A Senior Devops Engineer has advanced skills in DevOps engineering, including Software Engineering, Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
} \\ \hline
{3.10c.1}&{Front End Engineer / Senior Front End Engineer - NOIRLab}&{Front-end engineers with strong javascript skills, web services architecture, user interface design and astronomical search and visualisation to focus on the Science Platform portal. At least one of these FTEs needs to be at IPAC at a senior engineer level to reflect our current technical investment in Firefly and coordinate effort appropriately in conjunction with other IPAC Firefly development. An appropriately skilled FTE may be found elsewhere or may be added to an IPAC subcontract if available} \\ \hline
{3.10c.2}&{Front End Engineer / Senior Front End Engineer - IPAC}&{Front-end engineers with strong javascript skills, web services architecture, user interface design and astronomical search and visualisation to focus on the Science Platform portal. At least one of these FTEs needs to be at IPAC at a senior engineer level to reflect our current technical investment in Firefly and coordinate effort appropriately in conjunction with other IPAC Firefly development. An appropriately skilled FTE may be found elsewhere or may be added to an IPAC subcontract if available} \\ \hline
{3.10d.1}&{Science Platform \& Production Services Engineer}&{A Science Platform and Production Services Engineer is responsible for identifying and resolving  issues with production services, including user-facing services such as the Science Platform as well as facility services (such as deployments of the Science Platform at the telescope summit). They are also responsible for evolving services on the basis of rapidly changing user demand, for example the JupyterLab-based component of the Science Platform. They have strong software engineering skills including coding, testing and service deployment and can perform technical work in an independent manner.} \\ \hline
{3.10d.2}&{Services Architect / Senior DevOps Engineer}&{A Services Architect is a software engineer with advanced expertise in designing and building software services with particular regard to scalability, performance, deployment infrastructure and interface design. They are able to synthesize requirements, propose system architectures and independently implement services.
A Senior Devops Engineer has advanced skills in DevOps engineering, including Software Engineering, Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
} \\ \hline
{3.10e.1}&{Senior Scientific Programmer / Data Exploration Specialist}&{A Senior Scientific Programmer has deep domain expertise and is adept in capturing and implementing data analysis solutions. Their scientific background allows them to anticipate user data exploration needs and other requirements and to effectively communicate them to other engineers on their team.
A Data Exploration Specialist communicates data exploration needs to the engineers, documents and develops tools, demonstrates how to achieve scientific goals with the tools provided. This would explicitly include technical consultations to the Community Science Team and EPO scientists. Their scientific background allows them to translate the technical needs of the users of services (external and internal) into an engineering request, as well as functioning as liaison to other interrelated systems (in particular Middleware and Infrastructure) to which Science Platform services have a dependence.
} \\ \hline
{3.10e.2}&{Senior Devops Engineer / Data Engineer}&{A Senior Devops Engineer has advanced skills in DevOps engineering, including Software Engineering, Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
A Data Engineer is a software engineer with the ability to model and abstract data flow and representation, as well as design and implement appropriate systems for the effective curation and visualisation of particular kinds of data (eg. time series). 
A Data Exploration Specialist communicates data exploration needs to the engineers, documents and develops tools, demonstrates how to achieve scientific goals with the tools provided. This would explicitly include technical consultations to the Community Science Team and EPO scientists. Their scientific background allows them to translate the technical needs of the users of services (external and internal) into an engineering request, as well as functioning as liaison to other interrelated systems (in particular Middleware and Infrastructure) to which Science Platform services have a dependence.} \\ \hline
\end{longtable} \normalsize
