\normalsize \begin{longtable} {|p{0.05\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{USDF roles for Rubin Observatory Data Management Operations \label{tab:usdfroles}}\\ 
\hline 
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.2a}&{US Data Facility Lead}&{Provides management and oversight for the US Data Facility. Provides for evolution of service architecture and supporting ITC. Responsible for design and evolution of the US DF and its interactions with the French and UK Data Facilities, and the Chilean and other DACs.} \\ \hline
{3.2b.2}&{US DF Technical Lead - SLAC}&{Responsible for leading the Data, Compute and IT Security team involved in providing foundational services for file-based data, data resident in database engines, and facility-wide services including AAA and operational network security infrastructure.} \\ \hline
{3.2b.1}&{US DF Technical Lead - NOIRLab}&{Responsible for leading the Data, Compute and IT Security team involved in providing foundational services for file-based data, data resident in database engines, and facility-wide services including AAA and operational network security infrastructure.} \\ \hline
{3.2c}&{DF/IDACs Technical Coordinator}&{Coordinate technical needs among the collection of Data Facilities and IDACS. Respond to issues that come up day to day in connections, transfers etc.} \\ \hline
{3.2d}&{Data Movement Engineer}&{Maintain Rucio system which will be involved in the tracking and moving of data between multiple sites,including hosting environment for Rubin Observatory Data Space, Data Space batching services, and bulk export to other sites. This is in close conjunction with the Storage Engineers in the Data Facilities. Rucio is an open source HEP product which we have adopted on Rubin Observatory.} \\ \hline
{3.2e.3}&{Data Wrangler - IN2P3}&{The data wrangler ensures that data (science raw data, calibration data, data products, etc.) is replicated at IN2P3 and data products resulting from the local processing performed at IN2P3 are replicated to the USDF They also ensure that the data archived at IN2P3 and needed for the annual processing are recalled from tape on time for the image processing tasks to be performed. They ensure that the tools and systems used for replicating data at IN2P3 are operational. This role needs tight coordination with the team at the USDF that is responsible for data distribution.} \\ \hline
{3.2e.4}&{Data Wrangler - UK}&{The UK data wrangler ensures that data (science raw data, calibration data, data products, etc.) is replicated and data products resulting from the local processing performed in the UK are replicated to the USDF They also ensure that the data archived in the UK and needed for the annual processing are recalled from tape on time for the image processing tasks to be performed. They ensure that the tools and systems used for replicating data in the UK are operational. This role needs tight coordination with the team at the USDF that is responsible for data distribution.} \\ \hline
{3.2f.2}&{Database Administrator - SLAC}&{Administers QSERV, reformatted EFD, and other databases at the US Data Facility and Chilean Base Center. Makes sure the databases are backed up, properly interfaced to the authentication infrastructure. Interfaces with the Security Administrator to ensure access by only authorized users (confidentiality, integrity, and availability). Additional database responsibilities for supporting misc workflows and processes within the Data Facilities. The Database Administrator is also responsible for ensuring data transfers to disaster recovery stores are implemented and functioning according to policy. This assumes significant value engineering is realized by collecting miscellaneous databases into enterprise-level database, with potential additional savings by reusing database infrastructure for other database needs elsewhere in the project. Additional .5-1 FTEs otherwise.} \\ \hline
{3.2f.1}&{Database Administrator - NOIRLab}&{Administers QSERV, reformatted EFD, and other databases at the US Data Facility and Chilean Base Center. Makes sure the databases are backed up, properly interfaced to the authentication infrastructure. Interfaces with the Security Administrator to ensure access by only authorized users (confidentiality, integrity, and availability). Additional database responsibilities for supporting misc workflows and processes within the Data Facilities. The Database Administrator is also responsible for ensuring data transfers to disaster recovery stores are implemented and functioning according to policy. This assumes significant value engineering is realized by collecting miscellaneous databases into enterprise-level database, with potential additional savings by reusing database infrastructure for other database needs elsewhere in the project. Additional .5-1 FTEs otherwise.} \\ \hline
{3.2g.3}&{Catalog Manager - IN2P3}&{The catalog manager ensures the day-to-day operations of the astronomical catalog database at IN2P3. This includes ingesting new data and removing and archiving obsolete catalogs. They also interact with the data wrangler to ensure that the catalog data produced at other sites are imported and ingested into the IN2P3 catalog and that the catalog data produced at IN2P3 is ingested into the local catalog and replicated to other sites. They also ensure that the software releases for the catalog database are compatible with those releases used at other sites operating a catalog database, in particular, the USDF.} \\ \hline
{3.2g.4}&{Catalog Manager - UK}&{The catalog manager ensures the day-to-day operations of the astronomical catalog database at IN2P3. This includes ingesting new data and removing and archiving obsolete catalogs. They also interact with the data wrangler to ensure that the catalog data produced at other sites are imported and ingested into the IN2P3 catalog and that the catalog data produced at IN2P3 is ingested into the local catalog and replicated to other sites. They also ensure that the software releases for the catalog database are compatible with those releases used at other sites operating a catalog database, in particular, the USDF.} \\ \hline
{3.2h}&{US DF Infrastructure Group Leader}&{Lead US DF Software Developer, coordinating activities of the US DF Infrastructure Group as well as participating in group's technical activity.} \\ \hline
{3.2i}&{US DF Network \& Core Services Engineer - SLAC}&{Provides network hardware and operational functionality used from a site's border router to Rubin Observatory end equipment. Collaborates with the security engineer and also IT services related to dynamic reallocation of US DF enclaves to support these functions with network features. Supplies higher-level network services as needed at each site, such as DNS, NTP, domain name registrations, netflows, and support for security. Provides Rubin S3DF enclave core services, including login services, name services, and environment maintenance.} \\ \hline
{3.2j}&{US DF Software Developer}&{General and broad computing skills, responding to the myriad of issues/needs that will come up - including via user support tickets. Provides workload management (eg kubernetes) of the clusters. Other skills to be drawn from python coding, web application development and deployment, continuous integration tooling (eg Jenkins), database expertise, code and I/O optimization. Some of the work involves maintaining and improving the builds for the various Data Management Operations software products. This includes fixing the continuous integration builds and improving the packaging system (currently aiming for Conda but could potentially move to another system over ten years). This part of the role would also support the observatory software builds which could potentially remain different to the Data Management Operations builds.} \\ \hline
{3.2k}&{Workflow/Load Management Engineer}&{Maintain smooth operation and configuration of workflow/workload tools for pipeline operation.} \\ \hline
{3.2l.3}&{Image Handler - IN2P3}&{The image handler ensures the image processing stages assigned to IN2P3 are performed on time. This person also ensures that the processing (e.g. software releases, configuration files, etc.) is compatible with what is agreed upon with the other processing sites, in particular with the USDF. They also ensure that IN2P3's image processing infrastructure (batch processing, workflow management system, etc.) is operational and correctly configured for LSST needs. They also ensure the day-to-day operations of the annual image processing campaign. This role needs tight coordination with the team in charge of image processing at the USDF.} \\ \hline
{3.2l.4}&{Image Handler - UK}&{The image handler ensures the image processing stages assigned to the UK are performed on time. This person also ensures that the processing (e.g. software releases, configuration files, etc.) is compatible with what is agreed upon with the other processing sites, in particular with the USDF. They also ensure that the UK's image processing infrastructure (batch processing, workflow management system, etc.) is operational and correctly configured for LSST needs. They also ensure the day-to-day operations of the annual image processing campaign. This role needs tight coordination with the team in charge of image processing at the USDF.} \\ \hline
{3.2m.2}&{US DF Network \& Core Services Engineer - NOIRLab}&{Provides network hardware and operational functionality used from a site's border router to Rubin Observatory end equipment. Collaborates with the security engineer and also IT services related to dynamic reallocation of US DF enclaves to support these functions with network features. Supplies higher-level network services as needed at each site, such as DNS, NTP, domain name registrations, netflows, and support for security. Provides Rubin S3DF enclave core services, including login services, name services, and environment maintenance.} \\ \hline
{3.2n}&{US DF Technician}&{Provides technical support for the Rubin US DF hardware at SLAC. Responsible for physical installation tasks: server racking, cabling and power. Lifecycle tasks include maintenance, troubleshooting and repair. Responsibilities may extend to monitoring and updating firmware.} \\ \hline
{3.2o}&{Wide Area Network Technical Manager}&{Responsible for providing coordination amongst and managing relationships with the four independent WAN operators. Acts as the interface for services provided to the US DF in the context of the WAN. Responsible for managing the risk associated with each WAN operator, including developing mitigation strategies and proposed project responses to credible risks. Leads the Joint Wide Area Network Working Group. Well connected to DOE ESNet.} \\ \hline
{3.2p}&{Wide Area Network Architect}&{Familiar with WAN implementation technologies generally available in the networks supporting the Rubin Observatory. Familiar with technology roadmap of the ESNet WAN provider. Synthesizes and evolves network techniques and provisioning supporting the Rubin Observatory mission, as network technology evolves. Drawn from staff of WAN groups but explicitly supported by and work in the context of the Rubin Observatory.} \\ \hline
{3.2q}&{AVS Engineer}&{The Alert Verification System Engineers will implement the algorithms for the AVS and agree with the Alert Production Pipeline Group on how to best integrate them in the system. This interface has not yet been agreed but will be developed during pre-operations and maintained and evolved in survey operations. The work includes monitoring the system and ensuring it meets the US federal agencies needs. The AVS Engineers will install and maintain the computer and network infrastructure to support data processing operations, ensure operations compliance with all DOE and US government cyber security requirements, and coordinate requirements compliance and the interface with other parts of the Rubin Operations team.} \\ \hline
\end{longtable} \normalsize
