\normalsize \begin{longtable} {|p{0.07\textwidth}|p{0.25\textwidth}|p{0.7\textwidth}|} \caption{V\&V  Roles for Rubin Observatory Data Management Operations \label{tab:vnvroles}}\\
\hline
\textbf{WBS}&\textbf{Role Title}&\textbf{Role Description} \\ \hline
{3.14}&{}&{Verify and validate the survey data products.} \\ \hline
{3.14a}&{Lead Verification and Validation Scientist}&{Responsible for driving the overall vision of V\&V activities including test automation strategy and system tests. Leads the specification, development and execution of all verification, validation and quality assurance of the Rubin Observatory data products.  Responsible for evaluating, understanding and quantifying the survey systematics. Leads the V\&V team, reports to the AD for System Performance.} \\ \hline
{3.14b.1}&{Production Scientist - Fermilab Ops}&{Responsible for processing and database ingestion of Prompt (Alert) Data Products. Expert in the technical operation of the Alerts pipeline. Address bottlenecks, failure modes. Responsible for processing and database ingestion of Batch (DRP) Data Products. This includes responsibility for: acting as the Scientific Code Liaison, hardware and software deployment, oversight and responsibility for processing execution, prompt SDQA and response, alert filtering service operations, and external (community) broker operations.} \\ \hline
{3.14b.1}&{Production Scientist - Fermilab Ops}&{Responsible for processing and database ingestion of Prompt (Alert) Data Products. Expert in the technical operation of the Alerts pipeline. Address bottlenecks, failure modes. Responsible for processing and database ingestion of Batch (DRP) Data Products. This includes responsibility for: acting as the Scientific Code Liaison, hardware and software deployment, oversight and responsibility for processing execution, prompt SDQA and response, alert filtering service operations, and external (community) broker operations.} \\ \hline
{3.14b.2}&{Production Scientist - IN2P3}&{Responsible for processing and database ingestion of Prompt (Alert) Data Products. Expert in the technical operation of the Alerts pipeline. Address bottlenecks, failure modes. Responsible for processing and database ingestion of Batch (DRP) Data Products. This includes responsibility for: acting as the Scientific Code Liaison, hardware and software deployment, oversight and responsibility for processing execution, prompt SDQA and response, alert filtering service operations, and external (community) broker operations.} \\ \hline
{3.14b.3}&{Production Scientist - UK}&{Responsible for processing and database ingestion of Prompt (Alert) Data Products. Expert in the technical operation of the Alerts pipeline. Address bottlenecks, failure modes. Responsible for processing and database ingestion of Batch (DRP) Data Products. This includes responsibility for: acting as the Scientific Code Liaison, hardware and software deployment, oversight and responsibility for processing execution, prompt SDQA and response, alert filtering service operations, and external (community) broker operations.} \\ \hline
{3.14b.4}&{Production Scientist - Fermilab Research}&{Responsible for processing and database ingestion of Prompt (Alert) Data Products. Expert in the technical operation of the Alerts pipeline. Address bottlenecks, failure modes. Responsible for processing and database ingestion of Batch (DRP) Data Products. This includes responsibility for: acting as the Scientific Code Liaison, hardware and software deployment, oversight and responsibility for processing execution, prompt SDQA and response, alert filtering service operations, and external (community) broker operations.} \\ \hline
{3.14c}&{SDQA Scientist for Alert Production}&{Evolves, documents, and verifies the SDQA analysis for the prompt data products (Alert Production). This position requires a Ph.D. level astronomer with astronomical survey experience. The SDQA scientist works with the Alert Production group.} \\ \hline
{3.14d.1}&{SDQA Scientist for Data Releases - Princeton}&{Evolves, documents, and verifies the SDQA analysis for the annual Data Release data products. This position requires a Ph.D. level astronomer with astronomical survey experience. The SDQA scientist works with the Data Release group.} \\ \hline
{3.14d.2}&{SDQA Scientist for Data Releases - UK}&{Evolves, documents, and verifies the SDQA analysis for the annual Data Release data products. This position requires a Ph.D. level astronomer with astronomical survey experience. The SDQA scientist works with the Data Release group.} \\ \hline
{3.14d.3}&{SDQA Scientist for Data Releases - SLAC}&{Evolves, documents, and verifies the SDQA analysis for the annual Data Release data products. This position requires a Ph.D. level astronomer with astronomical survey experience. The SDQA scientist works with the Data Release group.} \\ \hline
{3.14d.4}&{SDQA Scientist for Data Releases - NOIRLab}&{Evolves, documents, and verifies the SDQA analysis for the annual Data Release data products. This position requires a Ph.D. level astronomer with astronomical survey experience. The SDQA scientist works with the Data Release group.} \\ \hline
{3.14e.1}&{Data Release Systematics Scientist - BNL Ops}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14e.1}&{Data Release Systematics Scientist - BNL Ops}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14e.2}&{Data Release Systematics Scientist - NOIRLab}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on non-dark energy science (including solar system, transient universe and Milky Way science). These positions will contribute to documentation for Data Release data products.} \\ \hline
{3.14e.3}&{Data Release Systematics Scientist - BNL Res}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14e.4}&{Data Release Systematics Scientist - SLAC Ops}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14e.5}&{Data Release Systematics Scientist - SLAC Res}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14e.6}&{Data Release Systematics Scientist - Fermilab Ops}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14e.7}&{Data Release Systematics Scientist - Fermilab Res}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14e.8}&{Surge Data Release Systematics Scientist - UWisc}&{The Data Release Systematics Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience, or a software engineer with extensive astronomical and Rubin Observatory experience. Systematics Scientists are responsible for conducting analyses of image and catalog data needed to evaluate, understand, and quantify the systematics, with focus on dark energy science. These positions will contribute to documentation for Data Release data products. } \\ \hline
{3.14f}&{Data Visualization Engineer}&{Leads and consults on data visualization system across all departments. Documents and develops data visualization tools, demonstrates how to achieve scientific goals with the tools provided, produces example visualizations. Includes technical support in data visualization to the Community and EPO scientists. These are specialist software engineers with science backgrounds who can cater to the scientific needs of the users, and are deployed to the REO Outreach, RPF Community Science, and other operatins teams by RPF Mgmt. } \\ \hline
\end{longtable} \normalsize
